### 2014-12-09 tex/short_2015/body.tex
Before serious shrinking

\teaser{
  \centering
  \subfigure[Server-rendered (OpenGL)]{
    \includegraphics[width=.2\linewidth]{frview1.jpg}
  }
  \subfigure[Client-rendered proxy model (Google\newline Chrome, artifacts not subdued)]{
    \includegraphics[width=.2\linewidth]{frview2.jpg}
  }
  \subfigure[Client-rendered proxy model (Google\newline Chrome, artifacts subdued)]{
    \includegraphics[width=.2\linewidth]{frview2.jpg}
  }
  \caption{\label{fig:FRView} The oil reservoir viewer FRView, developed in the
  CloudViz project~\cite{cloudviz}, showing a server-rendered image and two
  client-rendered images of automatically generated proxy models. For~(b),
  parameters are chosen to highlight some artifacts (few and large splats
  without intra-splat texturing, displaying of skewed splats) while the second
  client-rendered image (c) has parameters chosen to make an optimal proxy
  geometry (many more splats, intra-splat texturing, discarding of skewed
  splats.)}
}

@@

\begin{abstract}
   We describe an algorithm and implementation of an automatic proxy model
   generation system for a client/server remote rendering setup. In this
   context, a {\em proxy model}, is a light-weight replacement of a main model
   that is much easier to manipulate and render. This proxy model is
   automatically derived from the main model. The client may be a {\em thin
   client}, \eg, a hand-held tablet. For our implementation we only assume the
   availability of WebGL and Javascript on this client. On the server side we
   make use of OpenGL and a web server. In situations where the rate of received
   images deteriorate due to low bandwith, high latency or long rendering times,
   the client displays the proxy model. The proxy geometry is computed from
   depth buffers bundled with rendered images from the server, and the algorithm
   is non-intrusive in that it requires no modification of the application or
   its data itself.
   % Husk: Skal vaere en blank linje nedenfor

\begin{classification} % according to http://www.acm.org/class/1998/
\CCScat{\textbf{FIX THIS}Computer Graphics}{I.3.3}{Picture/Image Generation}{Line and curve generation}
\end{classification}

@@

%\begin{figure}[htb]
%  \centering
%  \subfigure[Server-rendered (OpenGL)]{
%    \includegraphics[width=.47\linewidth]{frview1.jpg}
%  }
%  \subfigure[Client-rendered proxy model (Google Chrome)]{
%    \includegraphics[width=.47\linewidth]{frview2.jpg}
%  }
%  \caption{\label{fig:FRView} The oil reservoir viewer FRView \textbf{FIKS HER ref}, showing a
%  server-rendered image and a proxy geometry generated from this and the
%  accompanying depth buffer. Note that we have chosen parameters for the proxy
%  generation (small number of splats ($128^2$), forcing display of splats that
%  would normally be discarded) to emphasize rather than reduce artifacts, \eg,
%  the ragged edges, a few holes, and the oddly placed (and rendered) axis
%  indicator. \textbf{Flytte opp til teaser, tredje bilde: uten artifacter for aa
%  vise at det kan bli bra}}
%\end{figure}

@@

Our approach has some similarities to {\em image based rendering} (IBR)
techniques, with the difference that an important IBR problem would be the
reconstruction of a depth map from images, while we have access to the full
depth map from a rendering pass.  Another way to use depth maps similar to what
we do, is for ``immersive streaming'', see \eg,~\cite{ibr}, where focus is on
depth map compression, an issue that we also consider.

Common to many IBR-algorithms is also that of stitching together 3D or 2.5D
point clouds. We could also in principle do this for our 2.5D maps fetched from
the server, but it is not clear that the benefit would outweight the
cost. \marginpar{\textbf{REF?!}}

@@

Finally, we note that these 2.5D heightmaps are exactly what ``3D cameras''
(time-of-flight and other range image sensors) produce, but most authors
considering these are typically building more complex geometries before
visualization. % , see~\eg,~\cite{}
\marginpar{\textbf{REF?!}}

@@

\marginpar{\textbf{... samle avsnittene nedenfor og komprimere...}}

@@

This viewer utilizes several GLSL shaders to render reservoir cells and
boundaries ({\em corner point grids}), tubular wells etc., and operates in
general on a geometric model that is not trivial to reduce in complexity. The
model is typically also very large, meaning that rendering the full model on a
thin client is prohibitive. With the automatic proxy geometry, we can obtain
interactive frame rates with a limited connection from a very lightweight client
to the server. For a comparison of a server-rendered image and a client-rendered
proxy model that is slightly rotated on the client, see again Figure~\ref{fig:FRView}.

>>>>

\teaser{
  \centering
  \subfigure[Server-rendered (OpenGL)]{
    \includegraphics[width=0.3\linewidth, trim={1cm 1cm 1cm 1cm}, clip]{frviewb1.png}
  }
  \subfigure[Client-rendered (WebGL)]{
    \includegraphics[width=0.3\linewidth, trim={0 1cm 0 1.5cm}, clip]{frviewb2.png}
  }
  \subfigure[Client-rendered (WebGL)]{
    \includegraphics[width=0.3\linewidth, trim={0 1.5cm 0 2cm}, clip]{frviewb3.png}
    % The trim params: left lower right upper
  }
  \caption{\label{fig:FRView} The oil reservoir viewer FRView~\cite{cloudviz},
  showing one server-rendered and two client-rendered images of automatically
  generated and slightly rotated proxy models.  For~(b), parameters are chosen to produce the best
  possible image, and in~(c) we want to highlight artifacts and implementational
  details. See the text for further discussion of these.}
}

@@

\begin{abstract}
\color{red}
   We describe an algorithm and implementation of automatic proxy model
   generation for a client/server remote rendering setup. A {\em proxy model} is
   a light-weight version of a main 3D model that is cheaper to render. We
   automatically derive this from the main model. The client is typically a
   tablet, for which we only assume availability of WebGL and Javascript. The
   server makes use of OpenGL and a web server. When the rate of received
   server-rendered images deteriorate, the client renders the proxy model, which
   is computed from depth buffers bundled with rendered images from the
   server. This algorithm requires little modification of the application
   itself.
   % Husk: Skal vaere en blank linje nedenfor

\begin{classification} % according to http://www.acm.org/class/1998/
\CCScat{Computer Graphics}{I.3.5}{Computational Geometry and Object Modeling}{Geometric algorithms, languages, and systems}
% http://www.acm.org/about/class/ccs98-html
\end{classification}

@@

@@

Our approach has some similarities to {\em image based rendering} (IBR)
techniques, with the difference that an important IBR problem would be the
reconstruction of a depth map from images, while we have access to the full
depth map from a rendering pass.  Another way to use depth maps similar to what
we do, is for ``immersive streaming'', see \eg,~\cite{ibr}, where focus is on
depth map compression, an issue that we also consider. {\color{red}Another work
focused on similar streaming and geometry compression,
is~\cite{teler}. Also,~\cite{220764} contains some of the same ideas as our
work, with respect to image-based rendering accelleration.}

Common to many IBR-algorithms is also that of stitching together 3D or 2.5D
point clouds. We could also in principle do this for our 2.5D maps fetched from
the server, but it is not clear that the benefit would outweight the
cost.

@@

{\color{red}Finally, we note that these 2.5D heightmaps are exactly what ``3D cameras''
(time-of-flight and other range image sensors) produce, but most authors
considering these are typically building more complex geometries before
visualization.} % , see~\eg,~\cite{}
\marginpar{\textbf{REF?!}}

@@

{\color{red} ... samle avsnittene nedenfor og komprimere...}

@@

This viewer utilizes several GLSL shaders to render reservoir cells and
boundaries ({\em corner point grids}), tubular wells etc., and operates in
general on a geometric model that is not trivial to reduce in complexity. The
model is typically also very large, meaning that rendering the full model on a
thin client is prohibitive. With the automatic proxy geometry, we can obtain
interactive frame rates with a limited connection from a very lightweight client
to the server. For a comparison of a server-rendered image and a client-rendered
proxy model that is slightly rotated on the client, see again
Figure~\ref{fig:FRView}. {\color{red}In Figure~\ref{fig:FRView}~(a), the full
server-rendered image is shown, and in~(b) and~(c), a slightly (about 10
degrees) rotated proxy model is rendered on the client. In~(b), parameters are
chosen for best possible results, while in~(c), we want to highlight some
effects. For the latter, we have chosen a small number of non-overlapping
splats, which are also outlined. In this image, it is easy to spot areas not
well covered by any splats, and also some areas where the texture coordinate
transform $T$ does not produce optimal results.}
